Modelling BCG vaccination in the UK

### 2019-08-06 rmds/00-abstract.Rmd
review abstract + contribution

Surveillance data can help assess whether changes in vaccination policy have influenced incidence rates. I used surveillance data to determine whether those at school-age, or neonates, were directly affected by the policy change. I found the policy change was associated with increased notifications in the UK born but this was outweighed by a reduction in notifications in the non-UK born. \par

Statistical modelling is restricted by the available data. Therefore, I developed a dynamic model of TB, fit to available data, to forecast the impact of the policy change. Although the fit to the data was poor the forecasts suggested that continuing school-age vaccination reduced TB incidence compared with neonatal vaccination. Neonatal vaccination reduced incidence in children but had little impact on other age groups.\par

>>>>

Surveillance data can help assess whether changes in vaccination policy have influenced incidence rates. I used surveillance data to determine whether those at school-age, or neonates, were affected by the policy change. I found that the policy change was associated with increased notifications in the UK born but this was outweighed by a reduction in notifications in the non-UK born. \par

Statistical modelling is restricted by the available data. Therefore, I developed a dynamic model of TB, fit to available data, to forecast the impact of the policy change. Although the fit to the data was poor, the forecasts suggested that continuing school-age vaccination reduced TB incidence compared with neonatal vaccination. Neonatal vaccination reduced incidence in children but had little impact on other age groups.\par
